Approximate State Abstraction

### 2016-01-31 paper/paper.tex
Random push
results outline, taxi plots with different epsilon range

@@

@@

>>>>

\enote{Note somewhere why we selected these MDPs -- b/c a wide variety}

@@

\dnote{One thing we want to add is a description of how diverse these domains are!}
\dnote{Also put in a note that we're using a uniform weighting scheme}

@@

Here we discuss the results shown in states blah blah \dnote{Description of this section}.

\begin{itemize}
\item For $\epsilon > 0$, there are extremely useful abstractions to be made. Want to emphasize that with approximate knowledge of X, can still abstract effectively (point out Minefield + NChain both retain a very good policy from abstract MDP). This hits the learnable point.
\item Explain goal based/Taxi (regenerate plot for different scale of epsilon)
\item Possibly talk about stochasticity (low priority)
\item Explain Random behavior, smooth interpolation, mention randomness, etc.
\item Describe plots a bit (what is the y-axis?)
\end{itemize}
